%------------------------
% Resume in Latex
% Author : Michael Zappa
% Based off of: https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%------------FONT OPTIONS------------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%------------------------------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeJobHeading}[5]{
	\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		{\textbf{#1} $|$ \emph{#2}} & #3 \\
		\textit{\small#4} & \textit{\small #5} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		{\textbf{#1} $|$ \emph{#2}} & #3 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
	\begin{itemize}[leftmargin=0.15in, label={}]
		}
		\newcommand{\resumeSubHeadingListEnd}{
	\end{itemize}
}

\newcommand{\resumeItemListStart}{
	\begin{itemize}
		}
		\newcommand{\resumeItemListEnd}{
	\end{itemize}\vspace{-5pt}
}

%------------RESUME STARTS HERE------------

\begin{document}

\begin{center}
	\textbf{\Huge \scshape Michael Zappa} \\ \vspace{1pt}
	\small (+1) 952-388-7465 $|$
	\href{mailto:me@michzappa.com}{\underline{me@michzappa.com}} $|$
	% \href{https://gitlab.com/michzappa}{\underline{gitlab.com/michzappa}} $|$
	% \href{https://github.com/michzappa}{\underline{github.com/michzappa}}
	% \newline
	\href{https://michzappa.com}{\underline{michzappa.com}} $|$
	\href{https://www.linkedin.com/in/michael-zappa/}{\underline{linkedin.com/in/michael-zappa}}
    \break
    Available July 2023.
\end{center}

%------------EDUCATION------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Khoury College of Computer Sciences, Northeastern University}{Boston, MA}
{Bachelor of Science in Computer Science, Minor in Linguistics}{Aug. 2018 -- May 2023}
\resumeItemListStart
\resumeItem{GPA: 3.9/4.0, Dean's List all semesters, Honors Program.}
\resumeItem{Relevant Coursework: Software Engineering, Compilers, Computer Systems, Networks and Distributed Systems, Systems Security, Programming Languages, Object Oriented Design, Algorithms and Data Structures, Foundations of Cybersecurity.}
\resumeItem{Attended Dialogue of Civilization in the North of Ireland focused on the role of storytelling in community activism, conflict resolution, and conflicted identities.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%------------EXPERIENCE------------
\section{Experience}
\resumeSubHeadingListStart
\resumeJobHeading
{SDE Co-Op} {Java, Amazon Web Services} {July 2022 -- December 2022}
{Amazon Global Robotics}{Westborough, MA}
\resumeItemListStart
\resumeItem{Participated in organization-wide Innovation project concerning robotic movement.}
\resumeItem{Debugged production service issues and supported on-call teammates.}
\resumeItem{Performed critical load-balancer partition and migration for team's core service.}
\resumeItem{Took ownership of service on deprecation path; addressed risks, communicated with customers, began deletion.}
\resumeItem{Investigated and justified team-level decisions for service architecture.}
\resumeItem{Created, modified, and deleted alarms across multiple services and regions.}
\resumeItem{Engaged with the wider Amazon community, particularly in the open-source software arena.}
\resumeItemListEnd

\resumeJobHeading
{Software Developer Co-Op} {Ruby on Rails, Oracle SQL} {July 2021 -- January 2022}
{Smartleaf, Inc}{Boston, MA}
\resumeItemListStart
\resumeItem{Specified, implemented, and tested API endpoints requested by clients in the wealth management industry.}
\resumeItem{Patched sequence bug in Ruby database adapter when importing large batches of rows.}
\resumeItem{Conducted security audit and corresponding upgrades of Ruby and JavaScript dependencies.}
\resumeItem{Worked with internal wealth management team to fix third-party data transfer in production.}
\resumeItem{Created automated performance and A/B tests of application across different environments.}
\resumeItem{Coordinated release pipeline between developer and business teams.}
\resumeItem{Fulfilled client deliverables ahead of schedule.}
\resumeItem{Interviewed and onboarded new team members at multiple levels of seniority.}
% \resumeItem{Prepared application for transition from Oracle SQL to PostgreSQL.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%------------PROJECTS------------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Klox Language}} {Kotlin, Gradle} {August 2022 - September 2022}
\resumeItemListStart
\resumeItem{Implemented an interpreter{\textsuperscript{{\href{https://gitlab.com/michzappa/klox}{[{\color{red}1}]}}}} for the Lox programming language in Kotlin.}
\resumeItem{Extended language to include native lists and standard library.}
\resumeItem{Attempted additional compilation to Scheme, challenged by the difference in semantics between the two languages.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Web Development}} {TypeScript, Elixir, Node.js, React, Phoenix, SQL} {April 2020 -- August 2020}
\resumeItemListStart
\resumeItem{Led back-end and mobile development for an application{\textsuperscript{{\href{https://github.com/HuskyHunties}{[{\color{red}1}]}}}} to facilitate a 24-hour scavenger hunt.}
\resumeItem{Created multiple websites{\textsuperscript{{\href{https://gitlab.com/michzappa/fish-express}{[{\color{red}1}]}}{\href{https://gitlab.com/michzappa/fish-graphql}{[{\color{green}2}]}}{\href{https://gitlab.com/michzappa/fish-phoenix}{[{\color{blue}3}]}}{\href{https://gitlab.com/michzappa/fish-phoenix-live}{[{\color{cyan}4}]}}}} to play ``Fish'' card game with friends remotely during COVID-19 pandemic.}
\resumeItem{Implemented back-ends in Typescript and Elixir to serve REST APIs.}
\resumeItem{Developed front-ends using React/Phoenix/React Native.}
\resumeItemListEnd

% \resumeProjectHeading
% {\textbf{Husky Hunt Helper}} {TypeScript, Node.js, SQLite, React Native} {April 2020 -- August 2020}
% \resumeItemListStart
% \resumeItem{Led back-end and mobile development for a team creating a web/mobile app to facilitate the scavenger hunt put on by Northeastern University.}
% \resumeItem{Designed a web server to manage the uploading, categorizing, and reading of groups, paths, and clues.}
% \resumeItem{Developed mobile app to give directions to clues around Boston and upload photos to the server.}
% \resumeItemListEnd
% \resumeProjectHeading
% {\textbf{Fish Card Game(s)}} {Node.js, React, GraphQL, Elixir, Phoenix, PostgreSQL} {April 2020 -- August 2020}
% \resumeItemListStart
% \resumeItem{Created web apps to play ``Fish'' card game with friends remotely during COVID-19 pandemic.}
% \resumeItem{Implemented multiple REST web servers to process and store data using Express.js, GraphQL, and Phoenix.}
% \resumeItem{Developed front-end for REST servers using React.}
% \resumeItem{Utilized Phoenix LiveView to create an application with real-time view updates using built-in websockets.}
% \resumeItemListEnd
\resumeSubHeadingListEnd

%------------TECHNICAL SKILLS------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		            \textbf{Languages}{: Java, TypeScript, OCaml, Ruby, C/C++, SQL} \\
		            \textbf{OS}{: Linux, MacOS}
		      }}
\end{itemize}

%---------------INTERESTS------------
\section{Interests}
\resumeItemListStart
\resumeItem{Computing: Reproducible packages and systems, programming languages and compilers, formal verification.}
\resumeItem{Other: Linguistics and foreign languages, high fantasy novels, geography, rugby, motorsport.}
\resumeItemListEnd

%---------------------------------------------
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
